---
title: "Spawner-Recruit Model Escapement Goal Analysis Report"
author:
  - name: '`input$txt_title`'
date: '`r format(Sys.time(), "%d %B, %Y")`'

output: 
  word_document:
    fig_caption: true
    toc: true
    number_sections: true
#   mainfont: Times New Roman
    reference_docx: template.docx
params:
  title: NA
  texts: NA
  add: NA
  data: NA
  JAGS: NA
  tbl_sum: NA
  tbl_sumpost: NA
  tbl_brood: NA
  tbl_run: NA
  plt_runesc: NA
  plt_srt: NA
  plt_SR: NA
  plt_yield: NA
  plt_lnRS: NA
  plt_lnalphai: NA
  plt_predict: NA
  plt_residual: NA
  plt_msy_prof: NA
  plt_max_prof: NA
---

```{r,setup, echo=FALSE,include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.cap = TRUE,
  comment=NULL, dev='png',message=FALSE,background=NULL)
```

\newpage
```{r,title, echo=FALSE,include=FALSE}
  title <- paste(input$txt_title)
  text <- paste(input$txt_free)
```

# Project Description 
## Stock Name : `r params$title`

`r params$texts`

# Analyses Methods
## Data
```{r,datadesciption, echo=FALSE,include=FALSE}
  nyr <- input$sryears[2]-input$sryears[1]+1
  o.yrs <- paste(min(sr.data.0()$Yr),'to',max(sr.data.0()$Yr))
  yrs <- paste(input$sryears[1],'to',input$sryears[2])
  o.age <- c(min(o.age()),max(o.age()))
  pool  <- ifelse(params$data =='Run',
            ifelse(input$combage,
                   'combined to the next nearest age.',
                   'dropped and the remaining run age proportions were rescaled.'),
             '')
    
Run <- paste('The brood table (Table 1) and spawner-recruit data were constructed from the input run and age table. The original run ages were trimmed from',o.age[1],'to',o.age[2],'to from',input$rage[1],'to',input$rage[2],'(Table 2). The run proportions of the trimmed ages were',pool)
run <- ifelse(params$data =='Run',Run,'')
brood <- paste0(length(sr.data.0()$Yr),'years, ranging from ',o.yrs)
spr <- ifelse(params$data =='Run','The constructed','The input')
trim <- paste('In this model analysis, the original data were trimmed to',nyr,'years, ranging from',yrs,'.')
yy <- ifelse(nyr !=length(sr.data.0()$Yr),trim,'')
```

`r run` `r spr` spawner-recruit data consists of `r brood`. `r yy`

## Model Run 
```{r,modeldesciption, echo=FALSE,include=FALSE}
# Add parameters for data and model descriptions--------------------------------
  jpar <- params$JAGS
  madd <- ifelse(params$add=='ar1','AR(1) error',ifelse(params$add=='kf','time-variant alpha','standard'))
  ss <- ifelse(input$SS,'state-space','')
# Model priors 
  change.prior <- paste('The default alpha and beta prior ranges were modified to', input$lnapha[1],'-',input$lnapha[2],'for ln.alpha and',input$beta[1],'-',input$beta[2],'for beta,respectively.')
  cp <- ifelse(input$Priors,change.prior,'')
```  

A Bayesian `r madd` `r input$Model` `r ss` Spawner-Recruit model was run using JAGS. The model was run in `r jpar$n.chains` chains.  In each chain, a total of `r jpar$n.iter` iterations was run, of which the first `r jpar$n.burnin` were discarded (burn-in).  From the latter `r jpar$n.iter-jpar$n.burnin` iterations, posterior samples were taken at every `r jpar$n.thin`  iterations.  A total of `r jpar$n.sims` samples were saved for the posterior data analyses.   
Uniform priors with default rages were used (see Method section Table 1). `r cp`  For each chain the starting value were randomly selected from the prior ranges.

## Model Parameters 
```{r}
kable(jpar$summary,caption = "JAGS parameters summary.", digits = c(rep(3,8),0))
```
For each parameter, n.eff is a crude measure of effective sample size, and Rhat is the potential scale reduction factor (at convergence, Rhat=1).  

DIC info (using the rule, pD = var(deviance)/2)
pD = `r round(jpar$pD,2)` and DIC = `r round(jpar$DIC,2)` 
DIC is an estimate of expected predictive error (lower deviance is better).


## Biological Reference Parameters 
From the posteriors key biological reference parameters were calculated (See Method section). 

```{r }
kable(params$tbl_sumpost,caption = paste0("Spawner Recruit model parameters summary.")) 
```


```{r,results='asis',eval = (input$Remove_out)}
cat('## Outliers Removal')
```
```{r,results='asis',eval = (input$Remove_out)}
total <- sum(Ref_data_sum()$n,na.rm= TRUE)
sn <- Ref_data_sum()$n[dim(Ref_data_sum())[1]]
cat('Out of the total',total,'posterior samples ',sn,'samples were used for the escapement goal analyses')
kable(Ref_data_sum(),caption = paste0("Summary of posterior samples removed."))

```

\newpage
# Figures 
## Spawner and Recruit timeseries 

```{r,fig.dim = c(16,8),fig.cap = paste0("Figure 1. Spawner(Escapement) and brood year recruit, and Recruit per Spawner (R/S) ")}
# Run and Escapement time series plot 
params$plt_srt
```

```{r, results='asis', eval=(params$data=='Run')}
cat('## Run and Escapement')
```

```{r,echo=FALSE,eval=(params$data=='Run'),fig.dim = c(16,8),fig.cap = paste0("Figure 1. Run and escapement")}
# Run and Escapement time series plot 
params$plt_runesc
```

\newpage

```{r, results='asis', eval=(input$SR_plt)}
cat('## Spawner-Recruit Plot')
```
```{r,fig.dim = c(12,8),eval=(input$SR_plt),fig.cap = paste0("Spawner-recruit curve (sold line: median, dash mean).  Gray shade indicates ", input$CI,"% Bayesian ",input$Li," interval.")}
params$plt_SR
```

```{r, results='asis', eval=(input$YLD_plt)}
cat('## Yield Plot')
```
```{r,echo=FALSE, eval=(input$YLD_plt),fig.dim = c(12,8),fig.cap = paste0("Yierld curve (sold line: median, dash mean).  Gray shade indicates ", input$CI,"% Bayesian ",input$Li," interval."),fig.id = "Spawner and Yield"}
params$plt_yield
```


\newpage

# Model Diagnoses 
```{r, results='asis', eval=(input$lSR_plt)}
cat('## ln(R/S) Plot')
```
```{r,echo=FALSE,eval=(input$lSR_plt),fig.dim = c(12,8),fig.cap = paste0("ln(R/S)-Spawner linear plot.  Gray shade and dash lines indicate 95% Bayesian credible and prediction interval.")}
params$plt_lnRS
```



```{r, results='asis', eval=(input$Res_plt)}
cat('## Prediction Plot')
```
```{r,echo=FALSE,eval=(input$Res_plt),fig.dim = c(16,8),fig.cap = paste0("Figure . Predicted and observd recruit.")}
params$plt_predict
```

```{r, results='asis', eval=(input$Res_plt)}
cat('## Residual Plot')
```
```{r,echo=FALSE,eval=(input$Res_plt),fig.dim = c(16,8),fig.cap = paste0("Figure . Residual plot."),fig.id = "Residual Plot"}
params$plt_residual
```


```{r, results='asis', eval=(params$add=='kf')}
cat('## Time variant alpha')
```

```{r,echo=FALSE,eval=(params$add=='kf'),fig.dim = c(18,8),fig.cap = paste0("Figure 8. Time variant alpha."),fig.id = "Time variant allpha plot"}
params$plt_lnalphai
```


\newpage


```{r, results='asis', eval= (input$MSY_prof)}
#cat('\\newoage')
cat('## MSY Profile')
```
```{r,echo=FALSE,eval = (input$MSY_prof),fig.dim = c(16,8),fig.cap = paste0("MSY Profile Analyses plot. The lines indicate the probability of a specified escapement producing yield greater than x percent of the MSY.")}
params$plt_msy_prof
```


```{r, results='asis', eval=(input$MSR_prof)}
cat('## RMAX Profile')
```
```{r,echo=FALSE,eval = (input$MSR_prof) ,fig.dim = c(18,8),fig.cap = paste0("RMAX Profile Analyses plot. The lines indicate the probability of a specified escapement producing recruit greater than x percent of the RMAX.")}
params$plt_max_prof
```


```{r, results='asis', eval=(input$T_Yld_prof)}
cat('## Target Yield Profile')
```
```{r,echo=FALSE,eval = (input$T_Yld_prof) ,fig.dim = c(18,8),fig.cap = paste0("Target Yield Profile Analyses plot. The line indicate probability of a specified escapement producing yield greater than the target yield.")}
params$plt_max_prof
```


```{r, results='asis', eval=(input$T_Rec_prof)}
cat('## Target Recruit Profile')
```
```{r,echo=FALSE,eval = (input$T_Rec_prof) ,fig.dim = c(18,8),fig.cap = paste0("Target Recruit Profile Analyses plot. The line indicates a specified escapement producing recruit greater than the target recruit.")}
params$plt_max_prof
```


\newpage
# Tables 

## Spawner-Recruit Data 

```{r,echo=FALSE, }
table <- sr.data()
names(table)[1:3] <- c('Year','Spawner','Recruit')
kable(round(table[,1:3],0),caption = "Spawner-Rercuit data used for the analyses.")
```

```{r, child=if (params$data=='Run') 'run_table.Rmd'}
```

```{r, child=if (input$SREQ & input$Model=='Ricker') 'SR_Equations_Ricker.Rmd'}
```

```{r, child=if (input$SREQ) 'SR_Equations.Rmd'}
```

```{r, child=if (input$Model=='Beverton-Holt') 'SR_Equations_BH.Rmd'}
```

