```{r,datadesciption, echo=FALSE,include=FALSE}
# Original data year range
  runyr <- paste(min(params$tbl_data[,1]),'-',max(params$tbl_data[,1]))
# Original number of years
  n.yrs <- length(params$tbl_data[,1])
# Original Brood year range 
  byr <- ifelse(params$data != 'Escapement Only', 
                paste(min(data_sr.0()$Yr),'-',max(data_sr.0()$Yr)),'NA')
# Original n Brood year
  n.byrs <- ifelse(params$data != 'Escapement Only',length(data_sr.0()$Yr),'NA')
  # Trimmed n.years   
  rn.yrs <- input$sryears[2]-input$sryears[1]+1
  dif <- ifelse(params$data == 'Escapement Only',n.yrs != rn.yrs,n.byrs != rn.yrs)
# Trimmed year range
  rbyr <- ifelse(dif,paste(input$sryears[1],'-',input$sryears[2]),'No data trimming')
# Original Age range 
  obage <-ifelse(params$data =='Run',paste(min(o.age()),'-',max(o.age())),'NA')
  trimage <- params$data =='Run'& ((o.age[1]-input$rage[1])!=0|(o.age[2]-input$rage[2])!=0)
# Trimmed Age
  r.age <-ifelse(params$data =='Run',ifelse(trimage,paste(input$rage[1],'-',input$rage[2]),
                                            'No Age data trimming'),'NA')
# Age Trimming method  
  pool  <- ifelse(trimage,
            ifelse(input$combage,
                   'combined to the next nearest age.',
                   'dropped and the remaining run age proportions were rescaled.'),
             'NA')
    
Run <- paste('The brood table (Table 1) and spawner-recruit data were constructed from the input run and age table. The original run ages were trimmed from',o.age[1],'to',o.age[2],'to from',input$rage[1],'to',input$rage[2],'(Table 2). The run proportions of the trimmed ages were',pool)
run <- ifelse(params$data =='Run',Run,'')
brood <- paste0(length(data_sr.0()$Yr),'years, ranging from ',o.yrs)
spr <- ifelse(params$data =='Run','The constructed','The input')
trim <- paste('In this model analysis, the original data were trimmed to',nyr,'years, ranging from',yrs,'.')
yy <- ifelse(nyr !=length(data_sr.0()$Yr),trim,'')
tg <- ifelse(input$target=='md','Median Target','Mean Target')
```


```{r,modeldesciption, echo=FALSE,include=FALSE}
# Add parameters for data and model descriptions--------------------------------
  jpar <- params$JAGS
  madd <- ifelse(params$add=='ar1','AR(1) error',ifelse(params$add=='kf','time-variant alpha',' '))
  ss <- ifelse(SS(),'state-space','standard')
# Model priors 
  change.prior <- paste('The default alpha and beta prior ranges were modified to', input$lnapha[1],'-',input$lnapha[2],'for ln.alpha and',input$beta[1],'-',input$beta[2],'for beta,respectively.')
  cp <- ifelse(input$Priors,change.prior,'Default')
```  

## Data and Model Configurations 
**Data**  
**File name:  ** `r params$file`  
**Data Type:  **  `r params$data`  
**Year range:  ** `r yrange`    
**Age range:  ** `r obage`   

**Brood Data**
**Year range: **`r byr`  

**Data Modification**  
**Trimmed Year range: **`r rbyr`  
**Trimmed Age range:  ** `r rbage`   
**Age Pooling Method: ** `r pool`  




**Model**  
**SR Model:  ** `r input$Model`  
**SR Model Type:  ** `r ss`  
**SR Model addition:  ** `r madd`  

**Model Configuration**  
**Total Iteration:  ** `r jpar$n.iter`  
**Burn-in:  ** `r jpar$n.burnin`  
**Posterior:  ** `r jpar$n.iter-jpar$n.burnin`  
**Thinning:  ** `r jpar$n.thin`  
**Chains:  ** `r jpar$n.chains`  
**Total Posterior Samples: ** `r jpar$n.sims`  
**Change Default Priors:** `r cp`  

**SR Target ** `r tg` 

## Data
`r run` `r spr` spawner-recruit data consists of `r brood`. `r yy`



```{r,echo=FALSE,include=FALSE}
knitr::opts_chunk$set(echo = FALSE,comment=NULL, dev='png',fig.dim = c(9,6),dpi=600,message=FALSE,background=NULL)
#opts <- options(knitr.kable.NA = "")
```

```{r}
# Run and Escapement time series plot 
#runesc()
```


```{r,echo = FALSE, fig.cap = paste0("Figure 1.  Spawner-recruit curve (sold line: median, dash mean).  Gray shade indicates ", input$CI,"% Bayesian ",input$Li," interval.")}
params$plt_SR
```


```{r,echo = FALSE, fig.cap = paste0("Figure 2  Spawner-recruit curve (sold line: median, dash mean).  Gray shade indicates ", input$CI,"% Bayesian ",input$Li," interval.")}
params$plt_yield
```

```{r}
#smsy.prof()
#params$Plt_MSY_Prof
cat("Figure 3. MSY Profile Analyses plot. ")
```


```{r}
#smax.prof()
#params$Plt_MSR_Prof
cat("Figure 4. Smax Profile Analyses plot. ")
```



```{r,eval=(input$dataType=='Run')}
#kable(round(brood.out()$brood,0),caption = "Table 1. Input brood table .")
```


```{r,fig. }
cat("Table 2.  JAGS Model Summary output.")
print(run.JAGS())
```

```{r}
kable(run.JAGS()$summary,caption = "Table. JAGS summary",format="pandoc" ) 
```



```{r}
kable(params$Tbl_sum,caption = "Table 3.  Standard Spawner Recruit Analyses summary.  Note: outliers were removed.",format="pandoc" ) 
```



