# Analysis Methods
```{r,datadesciption, echo=FALSE,include=FALSE}
# Original data year range
runyr <- paste(min(params$tbl_data[,1]),'-',max(params$tbl_data[,1]))
# Original number of years
n.yrs <- length(params$tbl_data[,1])
# Original Brood year range 
byr <- ifelse(params$data != 'Escapement Only', 
              paste(min(data_sr.0()$Yr),'-',max(data_sr.0()$Yr)),'NA')
# Original n Brood year
n.byrs <- ifelse(params$data != 'Escapement Only',length(data_sr.0()$Yr),'NA')
# Trimmed n.years   
rn.yrs <- input$sryears[2]-input$sryears[1]+1
dif <- ifelse(params$data == 'Escapement Only',n.yrs != rn.yrs,n.byrs != rn.yrs)
# Trimmed year range
rbyr <- ifelse(dif,paste(input$sryears[1],'-',input$sryears[2]),'No data trimming')
# Original Age range 
obage <-ifelse(params$data =='Run',paste(min(o.age()),'-',max(o.age())),'NA')
trimage <- params$data =='Run'& ((o.age[1]-input$rage[1])!=0|(o.age[2]-input$rage[2])!=0)
# Trimmed Age
r.age <-ifelse(params$data =='Run',ifelse(trimage,paste(input$rage[1],'-',input$rage[2]),
                                          'No Age data trimming'),'NA')
# Age Trimming method  
pool  <- ifelse(trimage,
                ifelse(input$combage,
                       'combined to the next nearest age.',
                       'dropped and the remaining run age proportions were rescaled.'),
                'NA')

Run <- paste('The brood table (Table 1) and spawner-recruit data were constructed from the input run and age table. The original run ages were trimmed from',o.age[1],'to',o.age[2],'to from',input$rage[1],'to',input$rage[2],'(Table 2). The run proportions of the trimmed ages were',pool)
run <- ifelse(params$data =='Run',Run,'')
brood <- paste0(length(data_sr.0()$Yr),'years, ranging from ',o.yrs)
spr <- ifelse(params$data =='Run','The constructed','The input')
trim <- paste('In this model analysis, the original data were trimmed to',nyr,'years, ranging from',yrs,'.')
yy <- ifelse(nyr !=length(data_sr.0()$Yr),trim,'')
tg <- ifelse(input$target=='md','Median Target','Mean Target')
```

```{r,modeldesciption, echo=FALSE,include=FALSE}
# Add parameters for data and model descriptions--------------------------------
jpar <- params$JAGS
madd <- ifelse(params$add=='ar1','AR(1) error',ifelse(params$add=='kf','time-variant alpha',' '))
ss <- ifelse(SS(),'state-space','standard')
# Model priors 
change.prior <- paste('The default alpha and beta prior ranges were modified to', input$lnapha[1],'-',input$lnapha[2],'for ln.alpha and',input$beta[1],'-',input$beta[2],'for beta,respectively.')
cp <- ifelse(input$Priors,change.prior,'Default')
```  

## Data and Model Configurations 
**Data**  
  **File name:  ** `r params$file`  
**Data Type:  **  `r params$data`  
**Year range:  ** `r yrange`    
**Age range:  ** `r obage`   

**Brood Data**
  **Year range: **`r byr`  

**Data Modification**  
  **Trimmed Year range: **`r rbyr`  
**Trimmed Age range:  ** `r rbage`   
**Age Pooling Method: ** `r pool`  




**Model**  
  **SR Model:  ** `r input$Model`  
**SR Model Type:  ** `r ss`  
**SR Model addition:  ** `r madd`  

**Model Configuration**  
  **Total Iteration:  ** `r jpar$n.iter`  
**Burn-in:  ** `r jpar$n.burnin`  
**Posterior:  ** `r jpar$n.iter-jpar$n.burnin`  
**Thinning:  ** `r jpar$n.thin`  
**Chains:  ** `r jpar$n.chains`  
**Total Posterior Samples: ** `r jpar$n.sims`  
**Change Default Priors:** `r cp`  

**SR Target ** `r tg` 

## Data
`r run` `r spr` spawner-recruit data consists of `r brood`. `r yy`

## Model Run 

A Bayesian `r madd` `r input$Model` `r ss` Spawner-Recruit model was run using JAGS. The model was run in `r jpar$n.chains` chains.  In each chain, a total of `r jpar$n.iter` iterations was run, of which the first `r jpar$n.burnin` were discarded (burn-in).  From the latter `r jpar$n.iter-jpar$n.burnin` iterations, posterior samples were taken at every `r jpar$n.thin`  iterations.  A total of `r jpar$n.sims` samples were saved for the posterior data analyses.   
Uniform priors with default rages were used (see Method section Table 1). `r cp`  For each chain the starting value were randomly selected from the prior ranges.




## Model Parameters 
```{r}
kable(jpar$summary,caption = "JAGS parameters summary.", digits = c(rep(3,8),0))
```
For each parameter, n.eff is a crude measure of effective sample size, and Rhat is the potential scale reduction factor (at convergence, Rhat=1).  

DIC info (using the rule, pV = var(deviance)/2)
pV = `r round(jpar$pV,2)` and DIC = `r round(jpar$DIC,2)` 
DIC is an estimate of expected predictive error (lower deviance is better).


## Biological Reference Parameters 
From the posteriors key biological reference parameters were calculated (See Method section). 

```{r }
kable(params$tbl_sumpost,caption = paste0("Spawner Recruit model parameters summary.")) 
```


```{r,results='asis',eval = (input$Remove_out)}
cat('## Outliers Removal')
```
```{r,results='asis',eval = (input$Remove_out)}
total <- sum(Ref_data_sum()$n,na.rm= TRUE)
sn <- Ref_data_sum()$n[dim(Ref_data_sum())[1]]
cat('Out of the total',total,'posterior samples ',sn,'samples were used for the escapement goal analyses')
kable(Ref_data_sum(),caption = paste0("Summary of posterior samples removed."))

```

\newpage
# Figures 
## Spawner and Recruit timeseries 

```{r,echo=FALSE,fig.dim = c(16,8),fig.cap = paste0("Figure 1. Spawner(Escapement) and brood year recruit, and Recruit per Spawner (R/S) ")}
# Run and Escapement time series plot 
params$plt_srt+theme(text = element_text(family = "serif"))

```

```{r, results='asis', eval=(params$data=='Run')}
cat('## Run and Escapement')
```

```{r,echo=FALSE,eval=(params$data=='Run'),fig.dim = c(16,8),fig.cap = paste0("Figure 1. Run and escapement")}
# Run and Escapement time series plot 
params$plt_run+theme(text = element_text(family = "serif"))
```

\newpage

```{r, results='asis', eval=(input$SR_plt)}
cat('## Spawner-Recruit Plot')
```
```{r,echo=FALSE,fig.dim = c(12,8),eval=(input$SR_plt),fig.cap = paste0("Spawner-recruit curve (sold line: median, dash mean).  Gray shade indicates ", input$CI,"% Bayesian ",input$Li," interval.")}
params$plt_SR
```

```{r, results='asis', eval=(input$YLD_plt)}
cat('## Yield Plot')
```
```{r,echo=FALSE, eval=(input$YLD_plt),fig.dim = c(12,8),fig.cap = paste0("Yierld curve (sold line: median, dash mean).  Gray shade indicates ", input$CI,"% Bayesian ",input$Li," interval."),fig.id = "Spawner and Yield"}
params$plt_yield
```

\newpage

# Model Diagnoses 
```{r, results='asis', eval=(input$lSR_plt)}
cat('## ln(R/S) Plot')
```
```{r,echo=FALSE,eval=(input$lSR_plt),fig.dim = c(12,8),fig.cap = paste0("ln(R/S)-Spawner linear plot.  Gray shade and dash lines indicate 95% Bayesian credible and prediction interval.")}
params$plt_lnRS
```



```{r, results='asis', eval=(input$Res_plt)}
cat('## Prediction Plot')
```
```{r,echo=FALSE,eval=(input$Res_plt),fig.dim = c(16,8),fig.cap = paste0("Figure . Predicted and observd recruit.")}
params$plt_predict
```

```{r, results='asis', eval=(input$Res_plt)}
cat('## Residual Plot')
```
```{r,echo=FALSE,eval=(input$Res_plt),fig.dim = c(16,8),fig.cap = paste0("Figure . Residual plot."),fig.id = "Residual Plot"}
params$plt_residual
```


```{r, results='asis', eval=(params$add=='kf')}
cat('## Time variant alpha')
```

```{r,echo=FALSE,eval=(params$add=='kf'),fig.dim = c(18,8),fig.cap = paste0("Figure 8. Time variant alpha."),fig.id = "Time variant allpha plot"}
params$plt_lnalphai
```


\newpage


```{r, results='asis', eval= (input$MSY_prof)}
#cat('\\newoage')
cat('## MSY Profile')
```
```{r,echo=FALSE,eval = (input$MSY_prof),fig.dim = c(16,8),fig.cap = paste0("MSY Profile Analyses plot. The lines indicate the probability of a specified escapement producing yield greater than x percent of the MSY.")}
params$plt_msy_prof
```


```{r, results='asis', eval=(input$MSR_prof)}
cat('## RMAX Profile')
```
```{r,echo=FALSE,eval = (input$MSR_prof) ,fig.dim = c(18,8),fig.cap = paste0("RMAX Profile Analyses plot. The lines indicate the probability of a specified escapement producing recruit greater than x percent of the RMAX.")}
params$plt_max_prof
```


```{r, results='asis', eval=(input$T_Yld_prof)}
cat('## Target Yield Profile')
```
```{r,echo=FALSE,eval = (input$T_Yld_prof) ,fig.dim = c(18,8),fig.cap = paste0("Target Yield Profile Analyses plot. The line indicate probability of a specified escapement producing yield greater than the target yield.")}
params$plt_max_prof
```


```{r, results='asis', eval=(input$T_Rec_prof)}
cat('## Target Recruit Profile')
```
```{r,echo=FALSE,eval = (input$T_Rec_prof) ,fig.dim = c(18,8),fig.cap = paste0("Target Recruit Profile Analyses plot. The line indicates a specified escapement producing recruit greater than the target recruit.")}
params$plt_max_prof
```


\newpage
# Tables 

## Spawner-Recruit Data 

```{r,echo=FALSE, }
table <- data_sr()
names(table)[1:3] <- c('Year','Spawner','Recruit')
kable(round(table[,1:3],0),caption = "Spawner-Rercuit data used for the analyses.")
```

```{r, child=if (params$data=='Run') 'run_table.Rmd'}
```

```{r, child=if (input$SREQ & input$Model=='Ricker') 'SR_Equations_Ricker.Rmd'}
```

```{r, child=if (input$SREQ) 'SR_Equations.Rmd'}
```

```{r, child=if (input$Model=='Beverton-Holt') 'SR_Equations_BH.Rmd'}
```
