---
title: "Escapement Goal Analysis Report"
author:
  - name:
date: '`r format(Sys.time(), "%d %B, %Y")`'
mainfont: Times New Roman
output: 
  output: word_document
  reference_docx: template.docx
#  officedown::rdocx_document:
    
#    mapstyles:
#      Normal: ['First Paragraph']


---

```{r,echo=FALSE,include=FALSE}
knitr::opts_chunk$set(echo = FALSE,comment=NULL, dev='png',fig.dim = c(12,8),message=FALSE,background=NULL)
library(officedown)
library(officer)

fp <- fp_par(
  text.align = "center", 
  padding.bottom = 20, padding.top = 120, 
  border.bottom = fp_border())

ft <- fp_text(shading.color='#EFEFEF', bold = TRUE)
```



```{r}
# Run and Escapement time series plot 
runesc()
```


```{r,fig.cap = paste0("Figure 1. Spawner-recruit curve (sold line: median, dash mean).  Gray shade indicates ", input$CI,"% Bayesian ",input$Li," interval.")}
srplot()
```


```{r,fig.cap = paste0("Figure 2. Yierld curve (sold line: median, dash mean).  Gray shade indicates ", input$CI,"% Bayesian ",input$Li," interval.")}
yldplot()
```


```{r,fig.cap = paste0("Figure 3. MSY Profile Analyses plot.")}
plt.msy.prof.fig()
```


```{r,fig.cap = paste0("Figure 4. Smax Profile Analyses plot.")}
plt.max.prof.fig()
```




```{r,eval=(input$dataType=='Run')}
kable(round(brood.out()$brood,0),caption = "Table 1. Input brood table .")
```

```{r, fig.cap="Table 2.  JAGS Model Summary output."}
print(run.JAGS())
```


```{r}
kable(sumbayes(),caption = paste0("Table 3. ",model.name(),"Spawner Recruit model parameters summary.","beta x 10^-",Bayesdata()$d," Outliers were removed.") ) 
```


## Spawner-Recruit model 

Two Spawner-Recruit models are available:**Ricker** and **Beverton-Holt** 

### Ricker model 
$$R = \alpha Se^{-\beta S}e^{\varepsilon}$$

### Beverton-Holt model 
$$R = \frac{\alpha S}{1+\beta S}e^{\varepsilon}$$
where 
$$\varepsilon_{iid} \sim N(0,\sigma ^{2})$$


In fitting the model to data, the model was log-linearlized as 

**Ricker Model**
$$ln(R)= ln.\alpha -\beta s+ln(S)+\varepsilon$$

**Beverton-Holt Model**
$$ln(R)=ln.\alpha -ln(1+\beta s)+ln(S)+\varepsilon$$
where $ln.\alpha = ln(\alpha)$, $s = S\cdot{10}^{-d}$ and $d = Int(log(S))$.   

The data were fitted to 
$$ln(R) \sim N(\mu,{\sigma}^{2})$$
where $\mu$ is Ricker or Beverton-Holt Spawner-Recruit equations. In the equation the conversion of $S$ to $s$ makes $\beta$ to a range similar to the range of $ln.\alpha$,which is numerically more efficient to estimate parameters. 


#### AR(1) model option 
AR(1) model (First-order autoregression model) assumes that error is serially correlated or that the value of residual at time *t* is a linear function of the residual at time *t-1*.  

This is modeled as 
${\varepsilon_{t}}=\phi {\varepsilon_{t-1}}+{\nu_{t}}$ where ${\nu_{t}} \sim N(0,{\sigma _{\nu }}^{2})$

#### Time variant alpha model option  
Time variant alpha model assumes that alpha takes random walk process. 
$${ln(\alpha )_{t}}={ln(\alpha )_{t-1}}+{\omega_{t}}$$ 
where ${\omega_{t}} \sim N(0,{\sigma _{\omega }}^{2})$

#### Model Parameters and Priors 

|Parameter |   Prior    |    Note  |
|  ------- | -------:|-------:|
| $ln(\alpha)$  |  $ln(\alpha) \sim U(0,10)$ |  All models   | 
| $\beta$    |     $\beta \sim U(0,10)$  |  All models   | 
| $\sigma$    |      $\sigma \sim U(0,10)$  |  All models    | 
| $\phi$    |    $\phi \sim U(-1,1)$   |  **AR1 option**  | 
| $\varepsilon_{0}$ |     $\varepsilon_{0} \sim N(0,100)$     |**AR1 option**  | 
| $\sigma _{\omega}$|     $\sigma _{\omega} \sim U(0,10)$     |**TVA option**| 
---

The model was written in JAGS (), with default setting of 5000 burn-in, followed by 10000 simulation and samples were taken at every 5th simulation.  3 chains where starting values were selected randomly from the prior range (Table 3). 
                                                                      

#### Model Parameters based on expected mean vs. median recruit 
Under the assumption of lognormal distribution of recruit (R), $R \sim LN(ln(\mu),{\sigma}^{2})$ or $ln(R) \sim N(\mu,{\sigma}^{2})$, $\mu$ is an expected **Median Recruit**, and expected **Mean Recruit** is $\mu = exp(ln(\mu) + {\sigma}^{2}/2)$.

**statistical bias corrected alpha parameters**  $ln(\alpha.c) = ln(\alpha) + {\sigma}^{2}/2$ and $\alpha.c = \alpha e^{\frac{\sigma^{2}}{2}}$
for AR1 model, $ln(\alpha.c) = ln(\alpha)+ \frac{\sigma^{2}}{2(1-\phi^{2})}$ and $\alpha.c = \alpha e^{\frac{\sigma^{2}}{2(1-\phi^{2})}}$

**Ricker model**
$$Median(R) = \alpha Se^{-\beta S}$$
$$Mean(R) = \alpha.c Se^{-\beta S}$$

**Beverton-Holt model** 
$$Median(R) = \frac{\alpha S}{1+\beta S}$$
$$Mean(R) = \frac{\alpha.c S}{1+\beta S}$$

### Profile Analysis 
MSY-Rmax profiles analysis is aimed to fined a range of $S$ that will produce yield-recruit that are above q% of MSY-Rmax.  

calculate the probability of a given escapement producing an yield-recruit that are above q% of MSY-Rmax.  The MSY profile is calculated in following steps.  
* In each Bayesian sample of SR parameters (j) and given spawner range(S)
  * Calculate expected yield $Y_{j}(S_{i})$ and find the maximum yield (**MSY**) $Max(Y_{j})$
  * Assign $X_{i,j}$ to 1 if the expected yield is above the minimum q% of the MSY or 0 if otherwise
* At each escapement take the mean of X from all the simulation samples. 
* MSY Profile Range $S_{MSY}$ is a range of spawners such that the profile probability is above the minimum p% target. 

This is written as: 
**MSY based spawner profile**
$$P(S_{i}) =\frac{\sum_{j=1}^{n}X_{i,j}}{n}$$
where

$$
X_{i,j} = 
\begin{cases}
 1   & \quad\ Y_{j}(S_{i})\geq  q\cdot\ Max(Y_{j})\\
 0   & \quad\ otherwise
 \end{cases}
$$

MSY based Escapement Goal range is a range of S where P(S) is equal to and greater than the predefined p. 

$$\left \{ S_{MSY}\leftarrow \left [ S_{l}\: ,\:S_{u}  \right ]|P(S)\geq p \right \}$$

### Rmax Proile 
Rmax Profile calculates the probability of a given spawner size producing recruits that are above q% of Rmax.  **Note that Ricker SR model only.  Rmax does not exist in Beverton-Holt SR model.**   

The Rmax profile is calculated in following steps.  
* At each Bayesian samples SR parameters (j) and given spawner range(S)
  * Calculate expected recruit $R_{j}(S_{i})$ and find the maximum recruit (**Rmax**) $Max(R_{j})$
  * Assign $X_{i,j}$ to 1 if the expected recruit is above the minimum q% of the Rmax or 0 if otherwise
* At each escapement take the mean of X from all the simulation samples. 
* Rmax Profile Range $S_{max}$ is a range of spawners such that the profile probability is above the minimum p% target.  

This is written as: 
**Rmax based spawner profile**
$$P(S_{i}) =\frac{\sum_{j=1}^{n}X_{i,j}}{n}$$
where
$$
X_{i,j} = 
\begin{cases}
 1  & \quad\ R_{j}(S_{i})\geq  q\cdot\ Max(R_{j})\\
 0  & \quad\ othrewise
 \end{cases}
$$
Rmax based escapement goal range is a range of S where P(S) is equal to and greater than the predefined p. 

$$\left \{ S_{max}\leftarrow \left [ S_{l}\: ,\:S_{u}  \right ]|P(S)\geq p \right \}$$



